%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{About Me}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvparagraph}

I worked extensively with PHP, specifically the Laravel framework.

As I delved deeper into web development, I eventually switched to Ruby and Ruby on Rails.
Within this tech stack, I've utilized a variety of powerful gems, including Sidekiq, Devise, and Pundit.
To ensure high-quality code, I used the linter Rubocop with extensions Rubocop-Performance and Rubocop-Rails.

I have experience with PostgreSQL as well as MySQL and Redis for caching.
When I was working in an analytical company, I specialized in the column-oriented database \href{https://clickhouse.com/}{ClickHouse}.
I also possess strong SQL skills, able to structure and normalize relational databases with ease.

As a Linux user, I'm skilled in the Bash programming language and have developed a variety
of scripts, which you can check out in my \href{https://github.com/wittyjudge/dotfiles/tree/master/.local/bin}{dotfiles Github repository}.

I have experience in Lua with my \href{https://github.com/WIttyJudge/dotfiles/tree/master/.config/nvim}{Neovim config}, and that was a fun learning experience.

With my varied technical background, I'm confident that I would be a great fit for the position of Backend Engineer.
For more information about my experience and preferences, please check out my \href{https://github.com/wittyjudge}{Github account}.

\end{cvparagraph}
